---
title: "Project 3: samplepackage Tutorial"
author: "Yuxin Huang"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{samplepackage Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(samplepackage)
```

#Introduction

This package includes 4 part of functions, which are:
\begin{itemize}
\item my_t.test, A function can perform a one sample t test in R.
\item my_lm, A function can fit a linear model in R.
\item my_knn_cv,
\item my_rf_cv.
\end{itemize}

To introduce each function of our package, we should first install the sample package:
Install \texttt{samplepackage} using:
```{r, eval = FALSE}
devtools::install_github("YuxinHuang0723/samplepackage")
```

And We load other packages and data we need:
```{r, eval = FALSE}
library(samplepackage)
data("my_gapminder")
data("my_penguins")
```

#Part 2: my_t.test function

This function can perform a one sample t test in R. So here, we use the "lifeExp" data from my_gapminder data set to test three different hypothesis about the mean of "lifeExp". 

In first situation, we set the null hypothesis as: mean of the lifeExp from gapminder data set is equal to 60, and the alternative hypothesis is that the mean of the data set is not equal to 60. We run the my_t.test function and get a list of statistics about this test hypothesis:
```{r}
my_t.test(my_gapminder$lifeExp, "two.sided", 60)
```
We have our P value for this test is 0.09314, which is greater than our cut off p value 0.05. This comparison indicates that we fail to reject the null hypothesis and the mean of the lifeExp from the gapminder dataset is equal to 60. 



In second situation, we set the null hypothesis as: mean of the lifeExp from gapminder data set is equal to 60, and the alternative hypothesis is that the mean of the data set is greater than 60. We run the my_t.test function and get a list of statistics about this test hypothesis:
```{r}
my_t.test(my_gapminder$lifeExp, "greater", 60)
```
We have our P value for this test is 0.95343, which is greater than our cut off p value 0.05. This comparison indicates that we fail to reject the null hypothesis and the mean of the lifeExp from the gapminder data set is equal to 60.

In third situation, we set the null hypothesis as: mean of the lifeExp from gapminder data set is equal to 60, and the alternative hypothesis is that the mean of the data set is less than 60. We run the my_t.test function and get a list of statistics about this test hypothesis:
```{r}
my_t.test(my_gapminder$lifeExp, "less", 60)
```
We have our P value for this test is 0.04657, which is less than our cut off p value 0.05. This comparison indicates that we reject the null hypothesis and have the evidence to support our alternative hypothesis: the mean of lifeExp from the gapminder data set is less than 60.

#Part 3: my_lm function

This function can fit a lieaner model in R. So here, We take the data from gapminder as example. We use "lifeExp" as response variable and "gdpPercap" and "continent" as explanatory variables. 

First, we run the function and will get a summary data frame:
```{r}
my_lm(lifeExp ~ gdpPercap + continent, my_gapminder)
```

Let's take the gdpPercap's estimate as example to explain how to interpret the Estimate statistic in this data frame. First, the Estimate here represents the coefficient for gdpPercap. It means when other covariates are identical, the expected difference in the response between two observations differing by one unit in X is 47.88852.

Then we test a hypothesis test for the gadPercap coefficient. The null hypothesis is that the coefficient equals to zero. The alternative hypothesis is that the coefficient doesn't equal to zero. The Pr(>|t|)(which represent p value for the hypothesis test) for the gdpPercap is 2.478202e-98, which is mostly close to 0 and the cut off p value here is 0.05. So the P value for this hypothesis is less than the cut off p value. This comparison indicates that we reject the null hypothesis and have the evidence to support our alternative hypothesis: the coefficient doesn't equal to zero.

Finally, let plot the  Actual vs. Fitted values:
```{r}
#load the package which we need in order to run ggplot
#use matrix1 to store my_lm data statistics
matrix1 <- my_lm(lifeExp ~ gdpPercap + continent, my_gapminder)

#use real_lm to store lm() data statistics
real_lm <- lm(lifeExp ~ gdpPercap + continent, data = my_gapminder)

#calculate x and use x * estimate to get the actual value
x <- model.matrix(lifeExp ~ gdpPercap + continent, data = my_gapminder)
actual <- x %*% matrix1$Estimate

#use mod_fits to store the fitted value
mod_fits <- fitted(real_lm)
#create a data frame to store the actual value and fitted value
my_df <- data.frame(actual = actual , fitted = mod_fits)
#plot the actual vs fitted graph 
#using scatter plot to plot the graph 
graph1 <- ggplot2::ggplot(my_df, ggplot2::aes(x = fitted, y = actual)) +
  ggplot2::geom_point() +
  ggplot2::geom_abline(slope = 1, intercept = 0, col = "red", lty = 2) + 
  ggplot2::theme_bw(base_size = 15) +
  ggplot2::labs(x = "Fitted values", y = "Actual values", title = "Actual vs. Fitted")+
  ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5))
graph1
```
From the graph, we can see that the function fit the real data value very well. Since all the points are plotted on the red line. 
